---
title: "Assignment 1"
author: "Nguyen Dang Thanh"
date: "8/18/2020"
output: html_document
---

Data description:
Copy from tidytuesday repo: 

### Data Dictionary

# `gdpr_violations.tsv`

|variable         |class     |description |
|:----------------|:---------|:-----------|
|id               |integer   |Idetifier for fine/violation |
|picture          |character | SVG image of violation country flag |
|name             |character | Name of country where violation was enforced |
|price            |integer   | Fine price in Euros (€) |
|authority        |character | Authority that enacted the violation |
|date             |character | Date of violation |
|controller       |character | Controller of data - the violator |
|article_violated |character | Specific GDPR Article violated (see the `gdpr_text.tsv` data for specifics) |
|type             |character | Type of violation |
|source           |character | Original source (URL) of fine data |
|summary          |character | Summary of violation |

# `gdpr_text.tsv`

|variable      |class     |description |
|:-------------|:---------|:-----------|
|chapter       |double    | GDPR Chapter Number |
|chapter_title |character | Chapter title |
|article       |double    | GDPR Article number|
|article_title |character | Article title|
|sub_article   |double    | Sub article number |
|gdpr_text     |character | Raw text of article/subarticle|
|href          |character | URL to the raw text itself|


Data explore:
1. Some data dated back in 1970 -> No logic.
2. In 2019, Google is fined 50 million euro. This case is an outlier.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r lib}
library(tidyverse)
library(lubridate)
library(plotly)

```

```{r data}
gdpr_violations <- readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-21/gdpr_violations.tsv')


```

```{r}
gdpr_violations <- gdpr_violations %>% mutate(Date = as.Date(date, format = "%m/%d/%Y"),
                                              year = year(Date))
p1 <- gdpr_violations %>% filter(year > 2017) %>% ggplot(aes(x = Date, y = price, color = name ))+
  geom_point()

ggplotly(p1)
```
