---
title: "ETC5521 Assignment 1"
author:
- (Weihao Li)
- (Dang Thanh Nguyen)
- Brenwin Ang
- Muhammad Soban Qasim
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    citation_package: biblatex
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float:
      collapsed: yes
csl: apa-6th-edition.csl
subtitle: Fines or Taxes? Exploratory Data Analysis on General Data Protection Regulation
  Fines
team: cassowary
bibliography: ref.bib
biblio-style: authoryear-comp
link-citations: yes
---

<!-- CSS style for title page -->

<style type="text/css">

h1.title {
  text-align: center;
}
h3.subtitle {
  color: Darkred;
  text-align: center;
}
h4.author {
  color: black;
  text-align: center;
}
h4.date {
  color: black;
  text-align: center;
}
</style>

```{css, echo = FALSE}
body{
  font-family: Helvetica;
  font-size: 17pt;
}
/* Headers */
h1{
  font-size: 22pt;
}
h2,h3{
  font-size: 18pt;
}
```

```{r setup, include=FALSE}
#Set knitr option and system language for R kernel
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center")
Sys.setlocale("LC_ALL","English")

# load libraries
library(tidyverse)
library(lubridate)
library(kableExtra)
library(tidytext)
library(wordcloud2)
library(bookdown)
library(plotly)
library(rnaturalearth)
library(sf)
library(colorspace)
library(ggthemes)
library(widgetframe)
library(DT)
```


[This assignment is for ETC5521 Assignment 1 by Team `r rmarkdown::metadata$team` comprising of `r knitr::combine_words(rmarkdown::metadata$author)`.]{style="color:#006DAE;"}


# Introduction and motivation

General Data Protection Regulation (GDPR) is a regulation that came into effect on 25 May 2018. GDPR aims to "protect fundamental rights and freedoms of natural persons and in particular their right to the protection of personal data" [@regulation2016regulation]. GDPR imposes obligations onto organisations anywhere, so long they target or collect data related to people in EU.   

Due to its novelty in establishment, @tikkinen2018eu stated that it would be a challenge to companies who lack awareness of the GDPR’s practical implications. Inconsistent practical and technical implementation of GDPR in organisation dealings in EU could be anticipated. By August 2020, more than 49 companies have been fined at least 100 thousand euros. Most of these fines were issued to IT companies [@fine]. The most famous (& largest) of these is was the 50 million euros fine issued to Google in France lack of transparency in data consent policies. (@googlefine)

Meanwhile, @eufuture suggests that GDPR poses a political challenge in Europe's battle to its digital future - A balance had to be striked between overregulation and risk-taking entrepreneurship; which has implications on the economy. Besides, part of the reasons behind the GDPR establishment and the later digital services taxes imposed by major EU countries were an indication that EU was waving the flag of digital sovereignty. Thus, against digital hegemony, it may have unintentionally placed a bottleneck especially on IT companies.

Available data of GDPR fines from @Privacy-Affairs, allows for gaining insight into the privacy issues and examine any trends in violation of articles of GDPR. This dataset was originally adopted by @Tidy-Tuesday, which is a social weekly data project in R. [[github](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-04-21/readme.md)] We outline the workflow of data collection, data cleaning and data analysis in the following sections. 

# Limitations
A potential limitation of this research is a good proportion(about 10%) of controller names (violators)  are missing from the data set which introduces extra difficulties to draw accurate conclusions with respect to the company nationality and identity. 

Fines documented by @Privacy-Affairs pertains to fines made public hence many of the fines may not be present. This data set can be thought of as "high-profile" fines. 

 
# Data description

```{r}
# Source script and clean environment after running the script
if (!(file.exists("data/gdpr_text.tsv") & file.exists("data/gdpr_violations.tsv"))){
  source("scrapy.R")
  rm(list = ls())
  detach("package:rvest", unload=TRUE)
}
```

```{r data cleaning}
gdpr_text <- read_tsv("data/gdpr_text.tsv")

gdpr_vio <- read_tsv("data/gdpr_violations.tsv")

# Normal data cleaning
gdpr_vio <- gdpr_vio %>% 
  # set price <= 0 = NA; since; no fines given yet; in trial etc. 
  mutate(price = if_else(price <= 0, NA_real_, price)) %>%
  # change date from character to Date variable
  mutate(date = as.Date(date, "%m/%d/%Y")) %>%
  # rid; date < 2010; since; GDPR; not institutionalized 
  mutate(date = if_else(date < "2010-01-01", NA_Date_, date)) %>%
  # clean controller names
  mutate(controller = if_else(controller == "Google Inc.", "Google", controller)) %>%
  mutate(controller = if_else(tolower(controller) == "unknown company", "Company", controller)) %>%
  mutate(controller = if_else(tolower(controller) %in% c("unknown", "unknwon", "unknown organization", "not known", "not disclosed", "not available"), "Unknown", controller)) %>%
  mutate(controller = if_else(tolower(controller) == "tusla child and family agency", "Tusla", controller)) %>%
  mutate(controller = if_else(tolower(controller) == "telefonica", "Telefónica SA", controller)) %>%
  mutate(controller = if_else(controller == "Vodafone España, S.A.U.", "Vodafone Espana", controller)) %>%
  mutate(controller = if_else(controller == "Vodafone Espana", "Vodafone España", controller)) %>%
  mutate(controller = if_else(tolower(controller) == "telecommunication service provider", "Telecom company", controller)) %>%
  mutate(controller = if_else(controller %in% c("Private person", "Private person"), "Private individual", controller)) %>%
  mutate(controller = if_else(controller %in% c("A bank", "bank", "Bank (unknown)"), "Bank", controller)) %>%
  mutate(controller = if_else(controller == "A mayor", "Mayor", controller)) %>%
  mutate(controller = if_else(controller == "bank", "Bank", controller)) %>%
  mutate(article_violated = if_else(article_violated == "Failure to implement sufficient measures to ensure information security", "Art.32 GDPR", article_violated))
```

The data was scraped from @Privacy-Affairs by @Ellis-Hughes, which posted on @Tidy-Tuesday github repo. We slightly adapted the scripts and removed duplication of GDPR fines due to multiple sources. Data spans from 2018-05-12 to 2020-08-21. 

Abnormal values includes fines with 0 price, indicating ongoing trials and fines before the establishment of the GDPR (which are implausible values) are set NA. Records with missing date are also set to NA. We further process inconsistency in corporation names. There are a number of unnamed organizations fined by GDPR in the data set. These are labelled as "Unknown". 

The dataset has some limitations that can be identified by the (source @Privacy-Affairs)  
- Not all cases are presented in the dataset. The data only includes finalised cases and cases that are made public. This can lead to bias in further analysis.
- A number of controller(violators) are vaguely described, or not disclosed. This may lead to misunderstanding and bias in the analysis.

The data consist of two datasets:

1. `GDPR_Violations.tsv` contains information of `r nrow(gdpr_vio)` fines/penalties which data protection authorities (in EU) have imposed under GDPR. Variables includes the country(where violation enforced), authority, date of violation, fine price of violation in Euros(€). 
 
2. `GDPR_text.tsv` contains articles of GDPR (`r nrow(as_tibble(unique(gdpr_text$article)))` of them). Included are Chapter title, article number, artcile title and raw text of the article.

Each variable are detailed in next the Section (\@ref(datadic)).

## Data Dictionary {#datadic}

### `gdpr_violations.tsv`

|variable         |class     |description |
|:----------------|:--------|:----------|
|id               |integer   |Idetifier for fine/violation |
|picture          |character | SVG image of violation country flag |
|name             |character | Name of country where violation was enforced |
|price            |integer   | Fine price in Euros (€) |
|authority        |character | Authority that enacted the violation |
|date             |character | Date of violation |
|controller       |character | Controller of data - the violator |
|article_violated |character |Specific GDPR Article violated (see the `gdpr_text.tsv` data for specifics) |
|type             |character | Type of violation |
|source           |character | Original source (URL) of fine data |
|summary          |character | Summary of violation |

###  `gdpr_text.tsv`

|variable      |class     |description |
|:-------------|:---------|:-----------|
|chapter       |double    | GDPR Chapter Number |
|chapter_title |character | Chapter title |
|article       |double    | GDPR Article number|
|article_title |character | Article title|
|sub_article   |double    | Sub article number |
|gdpr_text     |character | Raw text of article/subarticle|
|href          |character | URL to the raw text itself|


## Research questions

The overall aim of this research is to examine the demographics in the application of the GDPR in practice since its implementation (in 25 May 2018) and unveil any prevalent privacy issues in EU's cyberspace.

Three secondary questions are addressed in this research:

1. What were the characteristics of GDPR fines across countries, time and corporations? Are certain corporations targets of GDPR authorities?  
2. Which articles and regulations were more likely to be violated? And how much they commonly charged?  

3. What were the key words in each article, especially articles referenced the most in GDPR fines? Does this mean anything such as particular privacy issues?


# Analysis and findings

## GDP violations across time since its implementation

```{r plot2, fig.cap="Monthly number of GDPR violations by year, 2018-2020"}
color_eu <- c("#0a0af5", # blue
           "#f50a0a", # red
           "#f5f50a") # yellow

# create theme
theme_eu <- theme(
  #background & panels
  plot.background = element_rect(fill = "#87adf1"),
  panel.background = element_rect(fill = "#87adf1"),
  
  # customize facet strip
  strip.background = element_rect(fill = "#87adf1"),
  strip.text.x = element_text(size = 14, colour = "white"),
  
  # customize plot title
  plot.title = element_text(size = 22, face = "bold", colour = "white"),
  
  # axes title and tick labels
  axis.title.y = element_text(colour = "white", size = 13),
  axis.title.x = element_text(colour = "white", size = 13)
)


gdpr_vio %>%
  filter(!is.na(date)) %>%
  ggplot() +
  # highlight bars with high no. of fines
  geom_bar(aes(factor(month(date)), fill = date >="2019-10-01" & date <="2020-03-31" | month(date) == 6 & year(date) == 2020)) +
  facet_wrap(~year(date)) +
  ylab("Number of Violations") +
  xlab("Month") +
  scale_fill_manual(values = c("#0a0af5", # blue
                               "#f50a0a")) + # red
  labs(title = "Number of GDPR Violations, 2018-2020") +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "none") +
  theme_bw() +
  guides(fill = FALSE) +
  theme_eu
```

Figure \@ref(fig:plot2) shows the number of GDPR fines dished out in for each month for years 2018-2020. Months where high number of GDPR fines imposed are highlighted red. The last quarter of 2019 and the first quarter of 2020 saw the highest number of GDPR violations, with a peak of 35 violators fined in March 2020.



```{r plot1, fig.cap="Boxplot of GDPR fines across time, 2018-2020"}
# Draws multiple boxplots on different layers to display different colors
plot1 <- gdpr_vio %>%
  filter(!is.na(date)) %>%
  ggplot() +
  geom_boxplot(aes(x = factor(month(date)), 
                   y = price), 
               outlier.color = "#f50a0a") +
  geom_boxplot(data = filter(gdpr_vio,
                             date<"2019-09-01" | date>"2020-04-01"),
               aes(x = factor(month(date)), 
                   y = price), 
               outlier.color = "#f50a0a") +
  geom_point(data = filter(filter(gdpr_vio, month(date) == 3, year(date) == 2020), 
                           price == min(price, na.rm = T)),
             aes(factor(month(date)), price)) +
  geom_text(data = filter(filter(gdpr_vio,
                                 date >= "2019-12-30" & date<="2020-04-01"), 
                           price > 4e+05),
             aes(x = factor(month(date)), 
                 y = price,
                 label = name), 
            size = 3, hjust = -0.3, vjust = 0) + 
  geom_text(data = filter(filter(gdpr_vio,
                                 date >= "2019-10-01" & date<="2019-12-29"), 
                           price > 1e+06),
             aes(factor(month(date)), price, label = name), size = 3, vjust = 0.3, hjust = 1) +
  ggrepel::geom_text_repel(data = filter(filter(gdpr_vio, date >= "2019-09-01"&date <= "2019-09-30"), 
                           price > 2e+05),
             aes(factor(month(date)), price, label = name), size = 3, vjust= 1) +
  facet_wrap(~year(date))+
  xlab("Month") + 
  ylab("log price") +
  scale_y_log10()  +
  ggtitle("Boxplot of GDPR fines across time, 2018-2020")  +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_eu +
  theme(strip.background = element_rect(colour = "black"),
        panel.background = element_rect(colour = "black")) 

plot1
  


```

Box plot in Figure \@ref(fig:plot1) looks accumulated price against time in a boxplot where median is shown. Log price was used to aid visualisation as price was an extremely skewed distribution. 

The distribution of mean fines were rather staggered across the months. However, a number of outliers surfaced (circled in red) mostly at the end and start of 2019 and 2020.

```{r outliers, fig.cap="Spatial location of outliers from 09,2019 - 03,2020"}
ne_countries(returnclass = "sf", country = c("Poland", "Germany", "Austria", "Italy", "Netherlands", "Sweden")) %>%
  ggplot() +
  geom_sf(aes(geometry = geometry)) +
  geom_sf_text(aes(label = name), size = 3) +
  coord_sf(xlim = c(0,25), ylim = c(35,70)) +
  ggtitle("Spatial location of outliers \nfrom End 2019 - Start 03/2020") +
  xlab("Longitude") +
  ylab("Latitude") +
  ggthemes::theme_map() +
  theme(plot.background = element_rect(fill = "#add8e6"),
        panel.background = element_rect(fill = "#add8e6"),
        legend.background = element_rect(fill = "#add8e6"),
        plot.title = element_text(size = 15),
        plot.subtitle = element_text(size = 30)) 
```

These outliers include Poland, Austria, Germany, Italy, Sweden and Netherlands. Inspecting the spatial patterns of these outliers in Figure \@ref(fig:outliers), these countries are all closely connected to one other. 


### Characteristics of GDPR violations across countries {#country}

```{r map, fig.height=8, fig.width=12, fig.align = "center", fig.cap = "Map of GDPR Accumulated Fines"}
# extract countries in data set
gdpr_countries <- gdpr_vio %>% 
  distinct(name) %>% 
  pull()

# get sf objects; filter to countries in data set
countries_sf <- ne_countries(country = c(gdpr_countries, 
                                         "Czechia"), # for Czech Republic
                             scale = "large",
                             returnclass = "sf") %>% 
  select(name, geometry, pop_est) %>% 
  mutate(name = replace(name, name == "Czechia", "Czech Republic")) %>% 
  mutate(centroid = st_centroid(geometry)) %>% 
  # provide centroid for country
  mutate(c.x = map_dbl(centroid, 1),
         c.y = map_dbl(centroid, 2)) 

# Group fines by country; merge with sf
countries_map <- gdpr_vio %>% 
  group_by(name) %>% 
  mutate(
    # sum fines in each country
    price_sum = sum(price, na.rm = TRUE),
    # price category
    price_cat = case_when(
      price_sum >= 0 & price_sum <= 10000 ~ "0-10K",
      price_sum > 10000 & price_sum <= 50000 ~ "10K-50K",
      price_sum > 50000 & price_sum <= 100000 ~ "50K-100K",
      price_sum > 10000 & price_sum <= 500000 ~ "100K-500K",
      price_sum > 500000 & price_sum <= 1000000 ~ "500K-1M",
      price_sum > 1000000 & price_sum <= 10000000 ~ "1M-10M",
      price_sum > 10000000 ~ ">10M")) %>% 
  select(name, price_sum, price_cat) %>% 
  distinct()

countries_map$price_cat <- factor(countries_map$price_cat, levels = c("0-10K", "10K-50K", "50K-100K", "100K-500K", "500K-1M", "1M-10M", ">10M"))

# copied Countries & coordinates data from https://developers.google.com/public-data/docs/canonical/countries_csv
centroids <- read_tsv("data/countries.tsv") %>% 
  select(longitude, latitude, name) %>% 
  inner_join(countries_map)
  

# join countries_map data set with geom info
countries_map <- left_join(countries_map, countries_sf, by = c("name")) %>% 
  inner_join(centroids)
  

countries_map %>% 
  ggplot() +
  geom_sf(aes(geometry = geometry,
              fill = price_cat,
              label = price_sum)) +
  # zoom in; by setting limits 
  coord_sf(xlim = c(-27.5, 37.5),
           ylim = c(32.5, 82.5),
           expand = FALSE) + # take; exact limits (xlim/ ylim)
  colorspace::scale_fill_discrete_sequential(palette = "Reds 3", 
                                            rev = TRUE)+
  labs(fill = "accumulated fine category",
       title = "Map of EU",
       subtitle = "Accumulated GDPR Fines") +
  theme_map() +
  theme(legend.position = "right") +
  geom_text(data = countries_map, 
            aes(label = name,
                x = longitude - 0.2,
                y = latitude),
            check_overlap = TRUE) +
  theme(plot.background = element_rect(fill = "#add8e6"),
        legend.background = element_rect(fill = "#add8e6"),
        plot.title = element_text(size = 55, colour = "white"),
        plot.subtitle = element_text(size = 30, colour = "white")) 
```

Figure \@ref(fig:map) depicts the accumulated GDPR fines in EU in each price categories made. 

A number of countries have fines less than €50,000 and a mix of countries in the categories upwards. Fines accumulated appear to be concentrated in the middle such as where populations are dense (e.g. France, Germany, Italy).  

```{r plot3, fig.cap="Boxplot of GDPR fines by country"}
gdpr_vio_box <- gdpr_vio %>% 
  group_by(name) %>% 
  mutate(
    # sum fines in each country
    price_sum = sum(price, na.rm = TRUE),
    # price category
    price_cat = case_when(
      price_sum >= 0 & price_sum <= 10000 ~ "0-10K",
      price_sum > 10000 & price_sum <= 50000 ~ "10K-50K",
      price_sum > 50000 & price_sum <= 100000 ~ "50K-100K",
      price_sum > 10000 & price_sum <= 500000 ~ "100K-500K",
      price_sum > 500000 & price_sum <= 1000000 ~ "500K-1M",
      price_sum > 1000000 & price_sum <= 10000000 ~ "1M-10M",
      price_sum > 10000000 ~ ">10M")) %>% 
  mutate(color = case_when(
    price_cat == "0-10K" ~ "#D8B2B3",
    price_cat == "10K-50K" ~ "#CD9B9C",
    price_cat == "50K-100K" ~ "#C08284",
    price_cat == "100K-500K" ~ "#B2686B",
    price_cat == "500K-1M" ~ "#A34C50",
    price_cat == "1M-10M" ~ "#922D33",
    price_cat == ">10M" ~ "#7F000D"
  ))

# sequential_hcl(n = 20, palette = "Reds 2")

gdpr_vio_box %>%
filter(!is.na(price)) %>%
ggplot() +
geom_boxplot(aes(x = price, 
                 y = fct_reorder(name, price),
                 color = I(color)),
             fatten = 4) +
  scale_x_log10() +
  labs(y = "Country", x = "Log Price") +
ggtitle("Boxplot of GDPR fines by country") +
theme(plot.title = element_text(hjust = 0.5)) +
  theme_eu
```

Boxplot in Figure \@ref(fig:plot3) is shaded according to the price categories in Figure \@ref(fig:map). It is not necessarily that a country with the highest accumulated fines(in €) has the most number of price dished out. For example, Netherlands has €3.49M in accumulated fines but has the highest median in fine price. (refer to \@ref(fig:plot4))

```{r plot4, fig.cap = "Number of GDPR violations by country, from 2018-2020"}
countries_count <- gdpr_vio %>% 
  group_by(name) %>% 
  summarize(no_of_fines = n(),
            acc_fine = sum(price, na.rm = TRUE)) %>% 
  # get population data
  inner_join(countries_map) %>% 
  select(name, pop_est, no_of_fines, acc_fine) %>% 
  mutate(fines_per_100k = round(100000*(no_of_fines/as.numeric(pop_est)),2)) %>% 
  mutate(acc_fine = case_when(
    acc_fine >= 1000000 ~ paste0("€", round(acc_fine/1000000, 2),"M"),
    acc_fine <= 1000000 ~ paste0("€", round(acc_fine/1000000, 2),"K")
  )) 


countries_count %>% 
  ggplot() +
  geom_point(aes(x = no_of_fines,
                 y = fct_reorder(name, no_of_fines)), # order countries; in terms of number of fines
             colour = "blue",
             size = 10) +
  geom_segment(aes(x = no_of_fines,
                   xend = 0,
                   y = name,
                   yend = name),
               colour = "blue") +
  labs(y = "country",
       x = "number of fines",
       subtitle = "per 100K population | accumulated fine") +
  geom_segment(aes(x = no_of_fines,
                   xend = 110,
                   y = name,
                   yend = name),
               alpha = 0.3) +
  geom_text(aes(x = no_of_fines,
                y = name,
                label = no_of_fines),
            colour = "white") +
  geom_text(aes(x = 115,
                y = name,
                label = fines_per_100k),
            size = 4,
            colour = "#f5f50a",
            face = "bold") +
  geom_text(aes(x = 135,
                y =  name,
                label = acc_fine),
            size = 4,
            colour = "#f5f50a",
            face = "bold") +
  annotate(geom = "text",
           x = 113,
           y = 31,
           label = "no of fines \nper 100k",
           colour = "#f5f50a",
           face = "bold") +
  annotate(geom = "Text",
           x = 50,
           y = 31,
           label = "Total Breaches",
           size = 4,
           colour = "#f5f50a",
           face = "bold") +
  annotate(geom = "text",
           x = 140,
           y = 31,
           label = "accumulated \nfine",
           size = 4,
           colour = "#f5f50a",
           face = "bold") +
  expand_limits(y = c(0,35),
                x = c(0, 145)) +
  ggtitle("Number of Fines") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15)) +
  theme_bw() +
  theme_eu +
  theme(panel.grid = element_blank(),
        axis.text.y = element_text(colour = "white"),
        axis.text.x = element_text(colour = "white"),
        plot.subtitle = element_text(colour = "white")) 
```

Figure \@ref(fig:plot4) demonstrates the number of fined GDPR violations by country from 2018 to 2020. It also shows number of fines per 100,000 people in the population and accumulated fines.  

Again, a disparity can be observed in the accumulated fine and number of fines. For example, in 14 fines, Italy raked up €57.15M in fine. On the other end of the spectrum. With 31 fines in Hungary, they only accumulated $0.52K in fines. In other words, authorities in some countries catch the "big fishes" while others go for volume. 

All country in the EU has less than 35 cases of GDPR fines except for Spain, which has nearly 100 cases. Some exorbitant fines can be seen such as France which accumulated 51M in 5 fines. 



### Characteristics of GDPR violations across corporations

Was certain corporations being targeted by GDPR authorities?
```{r table1}
# Detail table
table1 <- gdpr_vio %>%
  filter(!is.na(date)) %>%
  arrange(date) %>%
  group_by(controller) %>%
  summarise(total_price = sum(price, na.rm = TRUE), 
            count = n(), 
            countries = paste(unique(name), collapse = ", "),
            date = paste(unique(paste0(year(date), "-", month(date))), collapse = ", ")) %>%
  filter(!controller %in% c("Unknown", "Company", "Private individual", "Bank", "Telecom company", "Restaurant", "Hospital")) %>%
  arrange(desc(total_price))%>%
  head(10)
table1 %>%  knitr::kable(caption = "Largest cumulative GDPR fines by corporation",
               col.names = c("Controller", "Cumulative price", "Count", "Countries", "Date")) %>%
  row_spec(c(1,4,10), bold = T, color = "white", background = "#D7261E") %>%
  kable_styling(full_width = F, "hover") %>%
  footnote(general = "Companies with background in red are owned by corporations or individuals outside EU")

```
Table \@ref(tab:table1) shows us the information about the ten corporations that have accumulated the most fines since the introduction of GDPR. Notice only three of them are non-local corporations, which suggests we can not reject the hypothesis of multinational corporation is being fairly treated by GDPR. 

`r table1$controller[1]` was fined `r table1$count[1]` times and had to pay a fortune of `r table1$total_price[1]/1000000` million euros. It is worth notice that `r arrange(table1,desc(count))$controller[1]` was fined `r arrange(table1,desc(count))$count[1]` times, the highest number of financial penalties received. A closer look at the Britist telecommunication company is provided in table \@ref(tab:table2). We discovered another fact: Not only did Vodafone España	receive a very high number of fines, its branch, Vodafone ONO also receive 2 fines. Together, Vodafone violated the GDPR 21 times in Spain, which is a fifth of the country's total number of violations.

Overall, the last quarter of 2019 and the first quarter of 2020 saw the highest number of GDPR violations. Since the introduction of GDPR, most country has less than 30 violations, except for Spain. The country recorded about 100 GDPR financial penalties, 21 of which from Vodafone. It seems that Vodafone is targeted by the Spain authority.

> Most of the violating companies; were large companies; especially with large amount of data.


```{r table2}
# Vodafone only
gdpr_vio %>%
  filter(!is.na(date)) %>%
  filter(grepl("Vodafone", controller)) %>%
  select(date, name, controller, price) %>%
  group_by(controller, country = name) %>%
  summarise(total_price = sum(price, na.rm = T),
            count = n(),
            date = paste(unique(paste0(year(date), "-", month(date))), collapse = ", ")
            ) %>%
  knitr::kable(caption = "GDPR fines issued to Vodafone", 
               col.names = c("Controller", "Countries", "Cumulative_price", "Count", "Date")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Analysis of violated article

In this part, the researchers want to find out: Which articles and regulations were more likely to be violated? And how much they commonly charged?

Figure \@ref(fig:art-plot1) answer the first question. Article 5 - "Principles relating to processing of personal data", Article 6 - "Lawfulness of processing" and Article 32 - "Security of processing" are most likely to get violated by controllers. In fact, more than half of all violations are related to this three article. It indicates that the "Processing" of personal data in EU has issues, which lead to high number of violations. Further research could explore this issues and provide a more detail and clearer view.

```{r art-plot1, fig.cap = "Number of violations by GDPR articles"}
# Init a list
art_list <- list()

# Iterating all articles
for (i in 1:100){
  
  # Define a pattern
  txt <- paste0("art. ", i, " ")
  
  # Match patterns with vector of lower case string
  art_list[[i]] <- grepl(txt, tolower(gdpr_vio$article_violated), fixed = TRUE)
  
  # Define another pattern
  txt <- paste0("art. ", i, "(")
  
  # Match again and add them together (Note: TRUE = 1, FALSE = 0)
  art_list[[i]] <- art_list[[i]] + grepl(txt, tolower(gdpr_vio$article_violated), fixed = TRUE)
  txt <- paste0("art.", i, " ")
  art_list[[i]] <- art_list[[i]] + grepl(txt, tolower(gdpr_vio$article_violated), fixed = TRUE)
  txt <- paste0("art ", i, " ")
  art_list[[i]] <- art_list[[i]] + grepl(txt, tolower(gdpr_vio$article_violated), fixed = TRUE)
  
  # As long as it matches with any pattern above, mark it as TRUE
  art_list[[i]] <- art_list[[i]] > 0
}

# Add up all logical values for each article (lapply), unlist them as a vector
tibble(id = paste0("Art. ", 1:100), count = unlist(lapply(art_list, sum))) %>%
  filter(count > 0) %>%
  ggplot() +
  geom_bar(aes(y = fct_reorder(id, count), x = count, fill = count > 50), stat = "identity") +
  xlab("Number of violation") +
  ylab("Article number") +
  labs(title = "Number of GDPR violations by article") + 
  scale_fill_manual(values = c("navyblue", "#D7261E")) +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "none") +
  theme_bw() +
  guides(fill = FALSE) +
  theme_eu

```

Figure \@ref(fig:artfines) shows us violation of Article 5, 6 and 32 will lead to a relatively large fine, and with a high chance the amount of the fine will falls between 10000-100000 euros. 

```{r artfines, fig.cap="GDPR fines by article"}
# Init a list
price_list <- NULL

for (i in 1:100){
  # for each article, retrieve all prices from the GDPR fine dataset if they violate that article
  if (is.null(price_list)){
    # Init the data frame
    price_list <- data.frame(id = rep(i, length(gdpr_vio$price[art_list[[i]]])), price = gdpr_vio$price[art_list[[i]]])
  } else {
    # Bind prices together
    price_list <- bind_rows(price_list, data.frame(id = rep(i, length(gdpr_vio$price[art_list[[i]]])), price = gdpr_vio$price[art_list[[i]]]))
  }
}

# Sort boxplots by median price

price_list %>%
  filter(!is.na(price)) %>%
  group_by(id) %>%
  summarise(price = price, md = median(price)) %>%
  ungroup() %>%
  ggplot() +
  geom_boxplot(aes(price, y = fct_reorder(paste0("Art. ", id), md, .desc = T), col = id %in% c(5,6,32))) +
  scale_color_manual(values = c("grey35", "#D7261E")) +
  scale_x_log10() +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "none") +
  xlab("Price (log10 scale)") +
  ylab("Article number") +
  ggtitle("GDPR fines by article") +
  theme_eu
```


## Text mining GDPR articles

In this part, the researchers want to find out: What were the key words in each article, especially articles referenced the most in GDPR fines? How did it reflect the privacy issues in the EU?

```{r text mining}
# Create word frequency and anti join useless words
word_list <- gdpr_text %>%
  select(article, text = gdpr_text) %>%
  unnest_tokens(word, text) %>%
  group_by(article, word) %>%
  summarise(count = n()) %>%
  anti_join(stop_words, by = 'word') %>%
  filter(!grepl("\\d", word)) %>%
  arrange(article, desc(count))
```

### Overview of words in GDPR articles

Figure \@ref(fig:overall) reflects the key concerns in GDPR. From the word cloud, we can see some regular words related to law such as "article", "regulation", "paragraph" and "pursuant". We can also find words related to data governance, like "processing", "processor", "authority", "supervisory" and "commission". It seems like the GDPR provides a framework to govern the general data usage within EU and empower some authorities to supervise companies. More importantly, there are words explaining the spirit of GDPR, which are "freedom", "personal", "rights" and "public". It tells us GDPR concerns about the personal and public freedom. Besides, we feel surprise that "privacy" is not a key words in GDPR.

```{r overall, fig.cap="Word cloud of GDPR"}

# Drop article attribute
temp <- data.frame(word = word_list$word, count = word_list$count)

# Use the first 1200 words to build word cloud
temp <- temp %>%
  filter(!grepl("\\d", word)) %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  arrange(desc(count)) %>%
  head(1200)

wordcloud2(temp, size = 0.3)

```

### Words in Article 5, 6 and 32 respectively

In Table \@ref(tab:artmostword), there are words that repeatedly occurs. They are "data", "process", "personal" and "controller". It suggests the most common privacy issue in EU is illegal processing of personal data. We can also find the most different words are "access" in Article 32, "subject" in Article 6 and "purposes" and "manner" in Article 5. It reflects slightly different core topics in these 3 articles. Other than that, they are very similar overall. 

```{r artmostword}
# List the top 5 words
word_list %>%
  filter(article %in% c(5,6,32)) %>%
  filter(!grepl("\\d", word)) %>%
  arrange(article, desc(count)) %>%
  group_by(article) %>%
  summarise(word = word[1:5], count = count[1:5]) %>%
  knitr::kable(caption = "Top 5 most common words for article 5, 6 and 32 respectively") %>%
  row_spec(c(1:5,11:15), color = "black", background = "lightgrey") %>%
  kable_styling(full_width = T, "hover")
  
```


### Overview of trigrams in GDPR articles

```{r}
# Extract trigrams
word_list <- gdpr_text %>%
  select(article, text = gdpr_text) %>%
  unnest_tokens(trigram, text, token = 'ngrams', n = 3) %>%
  group_by(article, trigram) %>%
  summarise(count = n()) %>%
  separate(trigram, c('word1', 'word2', 'word3'), sep =' ') %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  filter(!word3 %in% stop_words$word) %>%
  unite(trigram, word1, word2, word3, sep =' ') %>%
  filter(!grepl("\\d", trigram)) %>%
  arrange(article, desc(count))
```

```{r}
dt_wordlist <- word_list %>% 
  arrange(-count) 

dt_wordlist <-  DT::datatable(dt_wordlist,
          extensions = c("Scroller",
                         "FixedColumns"),
          options = list(pageLength = 10,
                         scrollX= T,
                         scrollY = "200px"))

widgetframe::frameWidget(dt_wordlist)
```


Trigram analysis can often provide us with more useful information about a text document. Figure \@ref(fig:wordc2) provides us with very special "GDPR" words. We can see "data protection officer", which is probably the officer work for the authority, and "competent supervisory authority", which is probably referring to the data protection authority.

Notice that there is a term "binding corporate rules", this represents multinational corporations are allowed to transfer personal data in a intra-organizational manner. This rules increases the risk of potential leak of personal data on other nations outside EU.

Ignore these highly complicated article phrases, we can still find some interesting terms which we are familiar with. Like the one "historical research purpose". It suggests data analysis is under consideration of GDPR.


```{r wordc2, fig.cap="Word cloud of trigram in GDPR"}
# Drop article attribute
temp <- data.frame(word = word_list$trigram, count = word_list$count)

# Use the trigrams to build word cloud
temp <- temp %>%
  filter(!grepl("\\d", word)) %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  arrange(desc(count))

wordcloud2(temp, size = 0.2)
```


## Findings
The reports finds that since the introduction of GDPR, the period from October, 2019 to April, 2020 saw the largest number of (high-profile) GDPR violations. Overall, most country has less than 30 violations, except for Spain. The country recorded about 100 GDPR financial penalties, 21 of which from Vodafone. This points to disparity in each country's commitment in imposing GDPR. Des

Regarding to the General Data Protection Regulation, the report discovers that the most commonly violated GDPR's article are article 5, article 6 and article 32, All of which  focused on the "Processing" of personal data.  It indicates that the "Processing" of personal data in EU may have issues.

From this report, future research could consider focusing on the case of Spain and Vodafone Espana. The Britist telecommunication corporation received a fifth of the total financial penalties related to GDPR violations in Spain.  Clearly, the Spain authorities have their eyes set on Vodafone. 

Another research field that can be focused on is the issues in the "Processing" of personal data in EU. As the most commonly violated GDPR's article are all related to Processing of personal data, there seems to be issues in this field.


# Conclusion  

GDPR is one of the most widely touted regulation for personal data protection. From the characteristics of fines given out in countries in \@ref(country), there is a disparity in implementation - some countries catch the "big fishes" while some go for volumes. Most of the fines occur at the end the end of the year and first few months of a new year.

Besides, no such evidence supports that GDPR was generally used as an alternative to "digital service tax" against multinational corporations. However, one particular corporation, Vodafone, was a target of the Spanish Data Protection Authority multiple times, which might be a special case. Moreover, the GDPR fines revealed that the most serious privacy issue in EU is the processing of personal data.

With the regulation still in its novelty stage, it would be interesting to follow where it goes from here.

# Acknowledgement

Following R packages are used in producing this research:
- colorspace: @colorspace
- rmarkdown: @rmarkdown
- tidyverse: @tidyverse 
- kableExtra: @kableExtra 
- ggplot2: @ggplot2 
- plotly: @plotly 
- bookdown: @bookdown 
- wordcloud2: @wordcloud2 
- lubridate: @lubridate 
- tidytext: @tidytext
- rnaturalearth: @rna

# References

