---
title: "ETC5521 Assignment 1"
subtitle: "Fines or Taxes? Exploratory Data Analysis on General Data Protection Regulation Fines"
team: cassowary
author:
  - Weihao Li
  - Dang Nguyen
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r libra}
library(tidyverse)
library(lubridate)
```

[This assignment is for ETC5521 Assignment 1 by Team `r rmarkdown::metadata$team` comprising of `r knitr::combine_words(rmarkdown::metadata$author)`.]{style="color:#006DAE;"}


# Introduction and motivation

[FILL] Give the bigger picture of the data, and inspire the reader to learn more about the problem by reading your analysis. 

# Data description

```{r}
if (!(file.exists("data/gdpr_text.tsv") & file.exists("data/gdpr_violations.tsv"))){
  source("scrapy.R")
  rm(list = ls())
  detach("package:rvest", unload=TRUE)
}
```

```{r}
`+.default` <- .Primitive('+')
`+.character` <- paste0
`+` <- function(e1, e2) UseMethod('+')

gdpr_text <- read_tsv("data/gdpr_text.tsv")
gdpr_vio <- read_tsv("data/gdpr_violations.tsv")
```

The data is scraped from [Privacy Affairs] by [Ellis Hughes], posted on [Tidy Tuesday]. It collected data from 2018-05-12 to 2020-03-25. We adapted the scripts they used and removed duplication due to multiple sources. Besides, latest fines up to 2020-08-21 were collected.

The data consist of two smaller dataset:

1. `GDPR_Violations.tsv` contains information of `r nrow(gdpr_vio)` fines and penalties which data protection authorities in EU have imposed under EU General Data Protection Regulation (GDPR). The dataset contains variables including the country and authority, the date of violation, the fine price of violation in Euros, the controller that violate the rule, ... Detailed information of variable is presented below.
 
2. `GDPR_text.tsv` contains `r nrow(gdpr_text)` articles of actual GDPR legal document. 

## Data Dictionary

### `gdpr_violations.tsv`

|variable         |class     |description |
|:---------------|:--------|:----------|
|id               |integer   |Idetifier for fine/violation |
|picture          |character | SVG image of violation country flag |
|name             |character | Name of country where violation was enforced |
|price            |integer   | Fine price in Euros (€) |
|authority        |character | Authority that enacted the violation |
|date             |character | Date of violation |
|controller       |character | Controller of data - the violator |
|article_violated |character | Specific GDPR Article violated (see the `gdpr_text.tsv` data for specifics) |
|type             |character | Type of violation |
|source           |character | Original source (URL) of fine data |
|summary          |character | Summary of violation |

###  `gdpr_text.tsv`

|variable      |class     |description |
|:-------------|:---------|:-----------|
|chapter       |double    | GDPR Chapter Number |
|chapter_title |character | Chapter title |
|article       |double    | GDPR Article number|
|article_title |character | Article title|
|sub_article   |double    | Sub article number |
|gdpr_text     |character | Raw text of article/subarticle|
|href          |character | URL to the raw text itself|


## Research questions

The overall aim of this research is to reveal the privacy issues in cyberspace within the EU and examine whether General Data Protection Regulation fines were used as another type of "digital services tax" imposed on multinational technology corporations.

Three secondary questions are addressed in this research:

1. What were the characteristics of GDPR fines across countries, time and corporations? Did certain countries target certain corporations at certain time?
2. Which articles and regulations were more likely to be violated? And how much they commonly charged? Was there any article and regulation being abused?
3. What were the key arguments in each article, especially articles referenced the most in GDPR fines? How did it reflect the privacy issues in the EU?


# Analysis and findings

[FILL] Should include at least one plot or numerical summary for each of your questions, that helps the reader arrive at an answer. You should also write paragraphs describing the methods, summaries and findings. 

# References

[Privacy Affairs]

[Ellis Hughes]

[Tidy Tuesday]


[Privacy Affairs]: https://www.privacyaffairs.com/gdpr-fines/

[Ellis Hughes]: https://github.com/thebioengineer

[Tidy Tuesday]: https://github.com/rfordatascience/tidytuesday

